The Holy Hand Grenade of Antioch

### 2020-02-22 draft-camelot-holy-grenade.tex
fix: handle bcp

%% Temporary fixes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\let\bcp\relax% [bcp14]#...#

\usepackage{verbatim}
\newenvironment{sourcecode}{\verbatim}{\endverbatim}

@@

The instructions in the \textit{Book of Armaments} on the proper deployment
of the Holy Hand Grenade of Antioch \bcp{may} be summarized as
follows, although this summary \textbf{SHALL NOT} be used as a substitute
for a reading from the Book of Armaments:

@@

\begin{enumerate}
  \item Preamble: St Attila Benediction
  \item Feast of the People on Sundry Foods
    \begin{itemize}
      \item Lambs
      \item Sloths
      \item Carp
      \item Anchovies
      \item Orangutangs
      \item Breakfast Cereals
      \item Fruit Bats
      \item \textit{et hoc genus omne}
    \end{itemize}
  \item Take out the Holy Pin
  \item The Count
    \begin{enumerate}% TODO: [upperalpha]
      \item Count is to Three: no more, no less
      \item Not Four
      \item Nor Two, except if the count then proceeds to Three
      \item Five is Right Out
    \end{enumerate}
  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, \bcp{shall} snuff it
\end{enumerate}

>>>>

%% Temporary fixes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{verbatim}
\newenvironment{sourcecode}{\verbatim}{\endverbatim}

@@

The instructions in the \textit{Book of Armaments} on the proper deployment
of the Holy Hand Grenade of Antioch \att[bcp14]{may} be summarized as
follows, although this summary \textbf{SHALL NOT} be used as a substitute
for a reading from the Book of Armaments:

@@

\begin{enumerate}
  \item Preamble: St Attila Benediction
  \item Feast of the People on Sundry Foods
    \begin{itemize}
      \item Lambs
      \item Sloths
      \item Carp
      \item Anchovies
      \item Orangutangs
      \item Breakfast Cereals
      \item Fruit Bats
      \item \textit{et hoc genus omne}
    \end{itemize}
  \item Take out the Holy Pin
  \item The Count
    \begin{enumerate}% TODO: [upperalpha]
      \item Count is to Three: no more, no less
      \item Not Four
      \item Nor Two, except if the count then proceeds to Three
      \item Five is Right Out
    \end{enumerate}
  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, \att[bcp14]{shall} snuff it
\end{enumerate}
